Grounding the interaction: anchoring situated discourse in everyday human-robot interaction

### 2011-07-15 cover_letter.tex
Fixed some issues with biblio + added Sisbot2011 on SPARK
Addressed the question on the Open World Assumption

@@

\subsection{``please improve the quality of the references (sometimes, the
publisher is missing, sometimes capitalization is omitted, sometimes
abbreviations are used and sometimes full names''}

>>>>

The Open World assumption mainly allows us to model that we may not know
if a fact is true or not.

One very common example is the {\tt knowsAbout} predicate. This predicate
defines if some agent knows about some object.

It is important (especially for dialog) to be able to equally model that an agent knows or 
does not know about the object, or that the robot simply does not know if 
the human knows about it.

The Open World Assumption has important consequences on the reasoning
abilities of the system, since it prevents the classical "negation by 
failure" and leads to tighter modelling requirement to locally "close the
world" (for instance, the {\tt Color} class is defined as the equivalent of
the union of the 10 or so color instances we consider).

@@
